\documentclass{article}
\usepackage{setspace}

\begin{document}

\centerline{\sc \large The Only True and Living Church}
\vspace{.5pc}
\centerline{\sc Michael Ferguson}
\centerline{\sc 9 August 2015}
\vspace{.5pc}
\centerline{\scriptsize (adapted from ``What Is the Blueprint of Christ's Church'' by Elder Tad R. Callister)}
\vspace{6pc}

In the first section of the Doctrine and Covenants the Lord makes this bold and significant statement: ``[This is] the only true and living church upon the face of the whole earth''.\footnote{D\&C 1:30} This does not mean that other churches do not have some truth, for certainly they do. It does not mean that other churches do not render good, for they render much good. What it does mean is that this is the only church that has all the truth that has been revealed thus far in this dispensation. What evidence do we have of this assertion?

\section*{A Blueprint}
Recently my wife and I decided that we needed a bigger home for our growing family, so we found a lot on which to build. We worked with an architect to produce a blueprint that would best accommodate the needs of our family. We designed a large gathering area where our family, friends, and other invited guests could spend quality time enjoying each others' company. We included an area above the garage that could be used by our young children for wholesome play activities. The basement includes a large storage area that allows us to follow the direction of our prophet to keep food storage. These and other design elements were incorporated into a blueprint. Our home was then built pursuant to these plans.

As the home was being constructed, we occasionally submitted a change order that revised the blueprint. When the home was finally completed, it was in exact conformity with our blueprint. If you take our blueprint and match it against every home in the world, how many homes would it perfectly match? Only one---our home. There might be an occasional resemblance here and there, but foundation for foundation, room for room, and roofline for roofline, there would only be one home that perfectly matched the blueprint---our home.

\section*{Christ's Church}
If one desired to discover Christ's church today, he would want to match the spiritual blueprint found in the New Testament against every Christian church in the world until he discovered a church that matched the blueprint---organization for organization, teaching for teaching, ordinance for ordinance, fruit for fruit, and revelation for revelation. In doing so, he might find some churches that had some similarities---a teaching or two that overlapped, an ordinance that is the same, some offices that bear common names---but he will only find one church, The Church of Jesus Christ of Latter-day Saints, that matches the blueprint in every material respect. Now I would like to put that assertion to the test.

Let us assume that the blueprint of Christ church contains the following sections:
\begin{enumerate}
\item Organization of Christ's Church
\item Teachings of Christ's Church
\item Ordinances in Christ's Church
\item Fruits of Christ's Church
\item Divine Revelation
\end{enumerate}

Each of these items is evident in the Church of Jesus Christ of Latter-day Saints. For the purposes of this meeting and in the essence of time, I will focus only on the first attribute---the organization of Christ's church.

\subsection*{Organization}

\subsubsection*{Apostles and Prophets}
Christ's church was founded on apostles and prophets. When Paul was writing to some new members of the Church, he said that they were now ``built upon the foundation of the apostles and prophets, Jesus Christ himself being the chief corner stone.''\footnote{Ephesians 2:20}

The Apostles understood the imperative need to keep the Quorum of the Twelve Apostles intact. When one Apostle, such as Judas, died and a portion of the foundation was ``chipped away,'' the other 11 Apostles gathered together and chose a successor so that the foundation would be whole again.\footnote{see Acts 1:22--25}

This pattern evidenced the importance of maintaining a quorum of twelve Apostles. So important were these Apostles to the well-being of the Church that Paul declared how long we needed them. He said to the Ephesians, ``Till we all come in the unity of the faith.''\footnote{Ephesians 4:13} And then he explained why: So we would not be ``carried about with every wind of doctrine.''\footnote{Ephesians 4:14} Accordingly, the Apostles were critical to keeping the doctrine pure.

For this and other reasons the blueprint reveals that the apostles and prophets constituted the foundation of Christ's church. Do you know of any change order in the New Testament, any revelation that revised the blueprint and states that apostles are no longer needed? I don't. If that is the case, then Christ's true Church today should have apostles and prophets as its foundation.

\subsubsection*{Seventy}
In order to assist the Savior and His apostles in preaching the gospel to the world, the Savior chose other men, called Seventy, to prepare the way. We read of these Seventy in Luke, chapter 10. Do you know of a church today that matches this blueprint---that has the office of Seventy?

\subsubsection*{Other Priesthood Offices}
The blueprint of the New Testament reveals other officers that constituted part of the organization of Christ's church: bishops;\footnote{see 1 Timothy3; Titus 1:7} elders;\footnote{see Acts 14:23; Titus 1:5} deacons;\footnote{see Philippians 1:1} evangelists, meaning patriarchs; and pastors,\footnote{see Ephesians 4:11} meaning such men as bishops and stake presidents who preside over a flock.

The sixth article of faith of the Church makes reference to this blueprint: ``We believe in the same organization that existed in the Primitive Church, namely, apostles, prophets, pastors, teachers, evangelists, and so forth.''\footnote{Articles of Faith 1:6} In other words, we believe the current Church of Jesus Christ should have the same organization as existed in Christ's original Church, subject only to revelatory changes. Therefore, each of these offices is present in our Church today.

\subsubsection*{Manner of Selection}
How were Christ's apostles and other officers chosen? Did the Savior go to the finest theological schools of the time and select the highest-ranking students? He did not. Instead, the blueprint tells us that He chose Peter, a fisherman, and Matthew, a tax collector, and later Paul, a tentmaker. Each was chosen from the rank and file---in essence, it was a lay ministry. Today the Church has a quorum of twelve Apostles who are likewise chosen from the rank and file of the Church. One may be a teacher, another an engineer, another an attorney, and so on.

Did Christ's apostles and other officers make application for the ministry? They did not. The blueprint tells us how Christ selected His officers: ``Ye have not chosen me, but I have chosen you, and ordained you.''\footnote{John 15:16} When Christ ordained His apostles, what did He give them? Matthew and Luke record the answer: ``He gave them power''\footnote{Matthew 10:1}---the priesthood power to act in His name and to do His work. That is why the blueprint tells us ``the Son of man \ldots gave authority to his servants.''\footnote{Mark 13:34} Why? So they could act in His name with His endorsement. Every man who holds the priesthood of God in this church today can trace his priesthood authority back to Jesus Christ, the source of all authority and power, so that he, likewise, is entitled to Christ's endorsement---His stamp of approval---as is required by the blueprint.

\subsubsection*{Name of the Church}
What was the name of the church organized by Christ? If we are baptized in the name of Christ, if we pray in the name of Christ, if we are saved in the name of Christ, and if He is the founder and chief cornerstone of His church, what would you expect the name of His church to be? The Church of Jesus Christ. The Savior, when speaking to the people in Book of Mormon times, taught the underlying rationale as to why the Church needed to bear His name: ``And how be it my church save it be called in my name? For if a church be called in Moses' name then it be Moses' church; if if it be called in the name of a man then it be the church of a man; but if it be called in my name then it is my church, if it so be that they are built upon my gospel.''\footnote{3 Nephi 27:8}

In other words, we do not take upon us any other name than Jesus Christ. Accordingly, the blueprint teaches us that Christ's church should bear His name. It is not generally known that the Reformation had been in existence for over 300 years before the time of Joseph Smith and no one thought to name his church after Jesus Christ. Of course, since the time of Joseph Smith, others have followed suit.

\section*{Conclusion}
If one were to match the blueprint of Christ's original church against every church in the world today, he would find that point for point, organization for organization, it will only match one---The Church of Jesus Christ of Latter-day Saints. The same could be said for the teachings, ordinances, fruits, and revelations of the church.

One cannot have the doctrines and ordinances as restored through the Prophet Joseph Smith without accepting Joseph Smith and the underlying history that is the basis for such. They are inseparable. They go hand in hand. You cannot call the fruit good and the tree bad. The Savior taught this truth long ago: ``A good tree cannot bring forth evil fruit, neither can a corrupt tree bring forth good fruit.''\footnote{Matthew 7:18} Accordingly, if the doctrinal fruit is good, then the tree from which it sprang---Joseph Smith and the accompanying underlying history of those revealed truths---is likewise good. You cannot have one without the other.

If this church is not Christ's church, then why does this church have the same fruits as Christ's original church, namely, miracles and gifts of the Spirit, current revelation from apostles and prophets, angels and visions, a moral people, a missionary-minded people, and a people who are intensely family centered? 

Some questions are simply more important than others in discovering the truth. If you come to know that Joseph Smith restored the biblical teachings, organization, and ordinances of Christ's church, or if you come to know that the Book of Mormon is of divine origin, then you know that Joseph Smith is a prophet. And if Joseph Smith is a prophet, then this is the only true and living Church upon the face of the whole earth. At that point, other questions pale in comparison. All other questions to the contrary become immaterial. Why? Because you have already answered the key questions that are the foundational pillars for knowing the truth.

I bear witness that the Church bears Christ's name because it does have His approved organization, His teachings, His ordinances, His powers, His fruits, and His constant revelation, all of which are referred to in His divine blueprint.

\begin{quotation}
\noindent
God loved us so he sent his Son,\\
Christ Jesus, the atoning One,\\
to show us by the path he trod\\
the one and only way to God.\footnote{Edward P. Kimball, ``God Loved Us, So He Sent His Son'', LDS Hymnbook, no. 187}
\end{quotation}


\end{document}
